\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
Comments

ACM should develop tools to gather and publicize this data. As a first step,
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
  the right one? Link seems
  dead!  But Richard says ``As a reader, my first question is, how do I get
  access to this calculator? Can you cite this calculator in some way? It
  would be great to give a citation to where people can learn about it or
  use it, even if just, "To learn more about the calculator, e-mail xxx."''}\fi. 
Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.

>>>>

ACM should develop tools to gather and publicize this data. As a first step,
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
 the right one? Link seems
 dead!  But Richard says ``As a reader, my first question is, how do I get
 access to this calculator? Can you cite this calculator in some way? It
 would be great to give a citation to where people can learn about it or
 use it, even if just, "To learn more about the calculator, e-mail xxx"''}\fi. 
Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.
